---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(usethis)
library(gh)
library(glue)
knitr::opts_chunk$set(echo = TRUE,
                      eval = FALSE,
                      collapse = TRUE)
```

### Git workflow for issue/feature

Assume the following repository for Git/GH workflow: <https://github.com/MayaGans/ghapitest>

1.  New issue/feature is created (`add README #1`)\

2.  Create branch for feature/issue (`fix-01`)

    ``` bash
    git checkout -b fix-01
    ```

3.  Fix issue/implement feature (add, commit message `closes #1`)

    ``` bash
    git add . 
    git commit -m "closes #1"
    git push --set-upstream origin fix-01
    ```

4.  Submit PR for `#01`

    -   <https://github.com/MayaGans/ghapitest/issues/1>

5.  Request review for `#01`

6.  Comment and mark `#01` as reviewed

    -   Creates `#02`: <https://github.com/MayaGans/ghapitest/pull/2>

7.  "Merge pull request `#2` from `MayaGans/fix-01` closes `#01`"

    -   [`fd2f3da`](https://github.com/MayaGans/ghapitest/commit/fd2f3daed49f0ee245cc3aae26a05b60b79c1215)

> `#01` is closed, but not tested (or associated with any tests), so if we want to include a link to the *test* that's associated with an issue/feature, we create another issue (`#03`)

8.  Create branch to test `#01` (maybe `test-fix-01`?)

9.  Write/run test for issue/feature (`#01`)

10. Create pull request that closes issue `#3` (new branch name?)

11. Request review for `#03`...

12. Comment and mark `#03` as reviewed...

13. "Merge pull request `#4` from `MayaGans/<test-fix-01>` closes `#03`"

------------------------------------------------------------------------

### Traceability matrix:

| issue/feature | issue/feature completed by | system test | test completed by | pass/fail |
|----------|--------------------|----------|-----------------------|----------|
|               |                            |             |                   |           |
|               |                            |             |                   |           |
|               |                            |             |                   |           |


## Querying GitHub

The `gh` package will give us commits

```{r , eval=TRUE}
# this gives all commits in main only
rpo_commits <- gh("/repos/{owner}/{repo}/commits", 
   owner = "MayaGans", 
   repo = "ghapitest")
head(rpo_commits)
```

And comments

```{r , eval=TRUE}
# this returns comments (in GH) on PR
rpo_comments <- gh("/repos/{owner}/{repo}/pulls/comments", 
   owner = "MayaGans", 
   repo = "ghapitest")
head(rpo_comments)
```


## Examples of the `gh` package:

```{r gh-testing}
repos <- gh("GET /orgs/{org}/repos", org = "r-lib")
vapply(repos, "[[", "", "name")
gh("/users/{username}/repos/{repo}",
   username = "hadley",
   repo = "adv-r")
gh("/users/{username}/repos/{repo}",
   username = "hadley",
   repo = "adv-r")
gh("/repos/{owner}/{repo}/comments",
   owner = "hadley",
   repo = "adv-r")
```
